|

### 2020-05-11 paper/Manuscript.Rmd

author: #"`r source('authors_yaml.R')`"
 - name: "Caspar J. Van Lissa"
    institution: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
  - name: "Andreas M. Brandmaier"
    institution: "3,4"
  - name: "Loek Brinkman"
    institution: "2,5"
  - name: "Aaron Peikert"
    institution: "3,6"
  - name: "Barbara Vreede"
    institution: "7"

affiliation: #"`r source('affiliation_yaml.R')`"
  - id: "1"
    institution: "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
  - id: "2"
    institution: "Open Science Community Utrecht"
  - id: "3"
    institution: "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id: "4"
    institution: "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany and London, UK"
  - id: "5"
    institution: "UMC Utrecht"
  - id: "6"
    institution: "Humboldt-Universität zu Berlin"
  - id: "7"
    institution: "University Library Utrecht"

>>>>

author:
  - name: "Caspar J. Van Lissa"
    institution: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
  - name: "Andreas M. Brandmaier"
    institution: "3,4"
  - name: "Loek Brinkman"
    institution: "2,5"
  - name: "Aaron Peikert"
    institution: "3,6"
  - name: "Barbara Vreede"
    institution: "7"

affiliation:
  - id: "1"
    institution: "Utrecht University faculty of Social and Behavioral Sciences, department of Methodology & Statistics"
  - id: "2"
    institution: "Open Science Community Utrecht"
  - id: "3"
    institution: "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id: "4"
    institution: "Max Planck UCL Centre for Computational Psychiatry and Ageing Research, Berlin, Germany and London, UK"
  - id: "5"
    institution: "UMC Utrecht"
  - id: "6"
    institution: "Humboldt-Universitaet zu Berlin"
  - id: "7"
    institution: "University Library Utrecht"
